Put Your Money Where Your Mouth Is: Prediction Markets and Climate Change

### 2016-03-07 paper.Rmd
add figure of social network
fixed history plots to color by true model (co2 and tsi)

---
title: "Put Your Money Where Your Mouth Is: Prediction Markets and Climate Change"
author: "John J. Nay, Martin Van der Linden, Jonathan Gilligan"
date: "March 4, 2016"
output: 
  pdf_document:
    keep_tex: true
bibliography: library.bib
---
```{r fig_ref, echo=FALSE}
source("utils/fig_ref.R") # tabRef and figRef functions
source("utils/multi_plot.R")
``` 
```{r, caption_setting, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
library(knitr)
knit_hooks$set(htmlcap = function(before, options, envir) {
  if(!before) {
    paste('<p class="caption">',options$htmlcap,"</p>",sep="")
    }
    })
# small margins
knit_hooks$set(small_mar = function(before, options, envir) {
    if (before) par(mar = rep(0.0001, 4))  # smaller margins all around
})
# opts_chunk$set(dev="tiff", 
#                dev.args=list(compression="lzw", type="cairo"),
#                dpi=300)
```
```{r multi_plot, echo=FALSE}
source("utils/multi_plot.R")
library(ggplot2)
theme_set(theme_classic())
library(pander)
```

@@

>>>>

---
title: "Put Your Money Where Your Mouth Is: Prediction Markets and Climate Change"
author: "John J. Nay, Martin Van der Linden, Jonathan Gilligan"
date: "March 7, 2016"
output: 
  pdf_document:
    keep_tex: true
bibliography: library.bib
---
```{r fig_ref, echo=FALSE}
source("utils/fig_ref.R") # tabRef and figRef functions
source("utils/multi_plot.R")
``` 
```{r, caption_setting, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
library(knitr)
knit_hooks$set(htmlcap = function(before, options, envir) {
  if(!before) {
    paste('<p class="caption">',options$htmlcap,"</p>",sep="")
    }
    })
# small margins
knit_hooks$set(small_mar = function(before, options, envir) {
    if (before) par(mar = rep(0.0001, 4))  # smaller margins all around
})
# opts_chunk$set(dev="tiff", 
#                dev.args=list(compression="lzw", type="cairo"),
#                dpi=300)
```
```{r multi_plot, echo=FALSE}
source("utils/multi_plot.R")
library(ggplot2)
theme_set(theme_classic())
library(pander)
```

@@

![Network](output/network.pdf)
